---
title: "Rkeylog Vignette"
author: "Nicolas Ballier"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
#         css: mystyles.css
vignette: >
  %\VignetteIndexEntry{Rkeylog Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
This vignette describes the elementary functions required for keystroke analysis. Keyloggr : an R  package that includes functions to pre-process the linguistic analysis of keylogs.


# Introduction
Keylogs have mostly been used for typist authentication (Giot et al). This package explores some of the functionalities required for linguistic analysis. Three levels of complexity have been distinguished in this approach.
- The first series of analyses is limited to a static conception of keystrokes, which aims at reconstituting the intended texts. It enables the R user  to estimate chunks of typed speech and basically works at word level.(Future elaborate version will compute word duration in relation to the frequency of words in the two reference corpoora SUBTLEX and SUBTUS, using the Zipf scale ). The system implements the cleanNLP parsing, which allows the analysis of clustesr of words and of part of speech. 
- The second series of analyses works at the character level. 
- the third series of functions focuses on backspace and a dynamic representation of the typing process.  Language models at ngram levels are introduced at this stage, allowing the comparison a pressed key with the alternative keys, using conditional probailites.

## Importing functions

###Readkeylog : a function that imports keylogs/script outputs from the different keylog capture programs.
(with fuctionality that saves the output 
TODO ERIN : multi-platform comparison of existing output : create the function that imports datasets / script outputs,

##DATASETS: 
Not for public domain : fastest, smallest extractions of existing datasets. Our own productions as testbeds
(and multilingual examples) 


## DESCRIPTIVE ANALYSIS :
print the fastest and slowest sentences, display a boxplot of the duration of sentences
print timegraphs for a given setence 

##Chunkingdisplay
The function that displays text separators corresponding to given thresholds
Displaying the text corresponding to the input and allowing for its visualisation (with default legends) 
Define threshold in terms of words/ duration / number of syllables (with the various implemented algorithms)

##phraseological candidates
A function that returns the fastest cluster of words, giving n as a parameter for n-grams (trigram, four-grams, etc)

KeyloggR
An R package for the linguistic analysis of 
-	ISI / OSI : 
-	Computing typing speed : number of hits / second (including space and backspace)


## time graphs
provide time graphs and corresponding chunkc for a given text / sentence


# Clusters : the function that 

#RECTANGULAR DATA
Intended text () : the R function that returns the text meant t be types , where backspaces have   been cleaned.

# RECTANGUAR DATA
This displays the expected rectangular format proposed as output for each dataset
```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Note generate minimaltext data


###Syllable count ()
A script that converts texts into syllable counts
ERIN : TODO  document the precision of the algorithm based on your Phonology module paper.



###Search()
This function is meant to enable searches on regular expressions. To retrieve a similar pattern to compare time stamps and durations for comparable seuences

#### display characterkey fonts in the plot?


## Styles

# thresholding (tid, threshold= , punct = "TRUE"")
For a given tid (text typed by a typist), represent chunks of speech corresponding to the pause threshold given as input (in ms). The logic parameter 'punct' corresponds to

# n-gram for keys and language models

#VERSION 2.0 : analysing backspaces (dynamic)

## Mining processes : erasure
erasure() : prints, for each tid, a dataframe with the list of keys that have been erased, the corresponding duration of the erasure process (sums backspace suration) and the  three words before and three words after the erasure.
erasure (tid)

# LANGUAGE MODELS
perplexity
Compute perplexity and other statistics of the entire corpus.
word-scores
Display log probability scores of each word, in addition to sentence and corpus perplexities.
utterance-scores
Write just the log probability score of each utterance, one per line. This can be used for rescoring n-best lists.

# ngramr – an R package for Google Ngrams
https://www.r-bloggers.com/ngramr-an-r-package-for-google-ngrams/

# Copyright issues
You can use the package , which is distributed under standard GPL terms. 
^[Please refer to the following paper if you use this package : Anonymous.]

# REFERENCE SECTION
(paste from Erin's thesis)


### NB A reminder of the rarkdown syntax
math expressions, e.g. $Y = X\beta + \epsilon$

> "Here is an intersting quote for the paper."
([via](https://link-to-the-paper))


```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```


# Figures
The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.


